---
title: "Military Doctrines Dataset"
page-layout: full
format:
  html:
    html-math-method: katex
    css: styles.css
    citations-hover: true
    footnotes-hover: true
editor: visual
execute:
  echo: false
  warning: false
  cache: false
---

```{r}
library(leaflet)
library(dplyr)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(countrycode)
library(DT)
library(htmltools)
```

```{r knitr_options}
coverage_df <- read.csv("content/data_copy/country_year_coverage.csv")
metadata <- read.csv("content/data_copy/nss_metadata.csv")
```

The Military Doctrines dataset is a catalog of `r metadata |> nrow()` National Security Strategy (NSS) documents spanning `r metadata |> dplyr::summarise(dplyr::n_distinct(country_name)) |> dplyr::pull()` countries from `r metadata |> dplyr::summarize(min = min(year)) |> pull()` to `r metadata |> dplyr::summarize(max = max(year)) |> pull()`. The data are sourced from government websites and other online repositories in their original pdf format and are organized into machine-readable text and csv format, which you can browse and download from this website.

The Military Doctrines project is led by [J Andrés Gannon](http://jandresgannon.com/) of Vanderbilt University.

```{r}
# Get world map data as sf object
world_map <- ne_countries(scale = "medium", returnclass = "sf")

# Aggregate document counts by country
document_counts <- coverage_df %>%
  group_by(cname) %>%
  summarise(num_documents = sum(coded, na.rm = TRUE)) %>%
  ungroup()
```

```{r}
world_map <- world_map |> 
  mutate(cc_name = countrycode(sourcevar = name,
                               origin = "country.name.en.regex",  
                               destination = "cown")) |>
  mutate(name = case_when(
    name == "Micronesia" ~ "Federated States of Micronesia",
    name == "S. Sudan" ~ "South Sudan",
    name == "St. Vin. and Gren" ~ "St. Vincent & Grenadines",
    name == "Côte d'Ivoire" ~ "Ivory Coast", 
    name == "Dem. Rep. Congo" ~  "Democratic Republic of the Congo", 
    name == "Marshall Is." ~ "Marshall Islands",
    name == "Czechia" ~ "Czech Republic", 
    TRUE ~ name  # Keep other names unchanged
  ))
```

```{r}
country_match <- data.frame(
  cname = unique(coverage_df$cname),
  name = unique(coverage_df$cname)  
)
```

```{r}
doc_counts_matched <- document_counts %>%
  left_join(country_match, by = "cname")
```

```{r}
# Join with world map
world_data <- world_map %>%
  left_join(doc_counts_matched, by = c("name" = "name"))

# Replace NA values with 0 for countries with no documents
world_data$num_documents[is.na(world_data$num_documents)] <- 0

# Create color palette
bins <- c(0, 1, 5, 10, 20, 50, 100, Inf)
pal <- colorBin("Purples", domain = world_data$num_documents, bins = bins)

# Create the leaflet map
leaflet(world_data) %>%
  addTiles() %>%
  setView(lng = 0, lat = 30, zoom = 2) %>%
  addPolygons(
    fillColor = ~pal(num_documents),
    weight = 1,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 2,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE
    ),
    label = ~paste0(name, ": ", num_documents, " documents"),
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto"
    )
  ) %>%
  addLegend(
    position = "bottomright",
    pal = pal,
    values = ~num_documents,
    title = "Number of Documents",
    opacity = 0.7
  )
```
